---
title: "Assignment 3"
subtitle: "Almond Yield Profit Model"
date: last-modified
author: "Kyle Alves & Steven Mitchell"
format: 
  html:
    code-fold: true
    toc: true
    toc-location: left
    theme: sandstone
    background-color: "#f8f9fa"
    embed-resources: true
    self-contained-math: true
execute:
  echo: true
  warning: false
  message: false
editor: visual
---

# Develop a profit model for your almond yield

```{r setup}
#load libraries
library(dplyr)
library(tidyverse)
library(ggplot2)
library(here)
library(janitor)
library(purrr)
library(ggpubr)

#Bring in both models for profit yield and almond yield
source(here("R", "almond-yield.R"))
source(here("R", "almond-profit.R"))
```

```{r data}
# Load data, summarize monthly min temp and precip totals
clim_data <- read_delim(file = "clim.txt", delim = " ") |>
  group_by(year, month) %>%
  summarise(T = min(tmin_c),
            P = sum(precip))

# Make a data frame of minimum February temps
T <- clim_data %>% 
  filter(month == 2) %>% 
  select(year, T)

# Make a data frame of total January precip
P <- clim_data %>%
  filter(month == 1) %>% 
  select(year, P)

# Make a clean data frame 
clim_clean = data.frame(temp = T, precip = P) %>% 
  clean_names() %>% 
  select(-precip_year) %>% 
  rename(year = temp_year) %>% 
  rename(temp = temp_t) %>% 
  rename(precip = precip_p)

# Run the almond yield model 
clim_clean$ayield = almondyield(clim_clean$temp, clim_clean$precip)
```



# Apply the profit model to your almond yield model

```{r}
almond_profit

clim_clean$profit1 <- almond_profit(T = clim_clean$temp, P = clim_clean$precip)
```

# Perform a simple informal sensitivity analysis of almond yield profit using at least 2 parameters

## Visualize Inputs

```{r}
# Make some random distributions for precip and temp
clim_clean$temp_norm <- rnorm(mean = mean(clim_clean$temp), sd = 5, n = length(clim_clean$temp))
clim_clean$precip_norm <- rnorm(mean = mean(clim_clean$precip), sd = 5, n = length(clim_clean$precip))

ggplot(clim_clean, aes(x = year, y = temp_norm)) +
  geom_point(col = "blue") +
  labs(title = "True Temp (Blue) vs Randomly Generated Temp (Red)",
       x = "Year",
       y = "Temperature (C)") +
  geom_point(aes(y = temp),
                 col = "red") +
            theme_bw()

ggplot(clim_clean, aes(x = year, y = precip_norm)) +
  geom_point(col = "blue") +
  labs(title = "True Precip (Blue) vs Randomly Generated Precip (Red)",
       x = "Year",
       y = "Precipitation (mm)") +
  geom_point(aes(y = precip),
                 col = "red") +
            theme_bw()
```

## Sensitivty Analysis

```{r}
parms <- cbind.data.frame(T = clim_clean$temp_norm, 
                          P = clim_clean$precip_norm)




# now run our model for the parameters
results <- parms %>% 
  pmap(~ almond_profit(
    T = parms$T,
    P = parms$P,
  baseline_yield = 1.125, 
  ppt = 3000, 
  area = 100, 
  cost = 4000
  ))

results[[1]]
length(results)

# extract the mean yield for each year
mean_profit <- map_df(results, `[`, c("mean"))
mean_profit <- cbind.data.frame(mean_profit, parms)

ggplot(mean_profit, aes(x = T, y = mean,
                       col = P)) +
  geom_point() +
  labs(title = "Mean Profit vs Temperature",
       x = "Temperature (C)",
       y = "Mean Profit") +
  theme_bw()

ggplot(mean_profit, aes(x = P, y = mean,
                       col = T)) +
  geom_point() +
  labs(title = "Mean Profit vs Precipitation",
       x = "Precipitation (mm)",
       y = "Mean Profit") +
  theme_bw()
```


# Write a short paragraph 

Based on our models for almond yield and the profit model that the yields feed into, it appears that precipitation may play a larger role in profits than temperature. This is based on what appears to be a direct linear relationship between precipitation and profit, while temperature appears not to have a clear correlation.
